\chapter{Elba The Car}
The hybrid vehicle that was build upon was named Elba several years ago when it was still a pure electric vehicle. The platform has been continuously improved and altered to the complex hybrid that exist today. Each year Elba participates in Shell Eco Marathon as an "Urban Concept Vehicle".

\section{Introduction (?)}
\subsection{How it moves}
Elba combines one DC motor, one Brushless DC motor (BLDC) and a one-cylinder internal combustion engine; to provide torque to the rear right wheel, propelling the car forwards.
A single person can ride the car, that person is coincidentally, also the driver. 
The driver steers the car and decide upon a reference speed that the car should follow and has the option to decide what mode (what combination of motor and engine) that should be used at a specific time.

\subsection{Aim}
The aim of Elba is to provide a platform to perform various levels of projects for engineering students, while at the same time be allowed to compete in Shell Eco Marathon.

\subsection{Urban Concept Vehicle}
The group that Elba competes in is called Urban Concept Vehicle. The vehicles in this group has be closer in appearance to today's production type passenger cars and has to comply with the specific rules of Shell Eco-marathon for this group. These vehicles has to have common features as wind shield wiper, turn signals and a horn. Vehicles competing in this group will require "stop and go"-driving, which means that once every lap the vehicle needs to do a full stop. This is to further increase the resemblance with city driving.

\section{System Overview}
\subsection{Electronic Control Units}
The car has four electronic control units (ECUs) that are responsible for different parts of the car.

\begin{itemize}
\item Front-ECU
\item Back-ECU
\item ICE-ECU
\item Clutch-ECU
\end{itemize}

The Fornt-ECU is responsible for the human interface, the buttons where the driver is able to decide mode and speed if the car is in manual mode. It sends speed and dive mode on the can bus.

The Back-ECU controls the motors via the separate motor controllers. It has veto over the ICE and Cluch.

The internal combustion engine is controlled by the ICE-ECU and this is its only task. It senses the lambda value and motor? temperatures to control the injection of fuel.

The Cluch-ECU controls the clutch. It interfaces to two H-bridges which in turn steers the linear actuators.  

\subsection{Communication}
The car uses a CAN network to communicate between the distributed micro-controllers. The micro-controllers have specific values that are needed elsewhere; these are sent on the CAN-bus. 

Another CAN network is used between the Back-ECU and the inMotion driver that controls the brushless motor. This newtwork ustes the protocol CANopen that lies on top of the CAN bus.
The instrumentation panel communicates via Bluetooth with the data-logger/GPS-unit.

\subsection{Energy supply}
All energy used to propel the car forwards (during the competition) comes from the ethanol fuel, but electrical energy can be stored in the super-capacitor. When the electrical motors generate energy it can be stored in this super-capacitor for later use. The car can only start from standstill using one of the electrical motors with energy from the super-capacitor.  

\section{Requirements}
\subsection{Rules}
At Shell Eco Marathon all vehicles must pass two inspections before the vehicle is allowed to enter the track. First a safety inspection evaluating if it's dangerous to have the vehicle on the track, both for the driver and other vehicles. And second a technical inspection asserting if the vehicle complies with the competition rules.

\section{Design decisions}
\subsection{Clutch decisions}
One of the major problems with the car has been the clutch. To solve the mechanical problems it was decided to appoint one team from the machine design department to work solely on the mechanical parts of the clutch. The mechatronics team decided to completely remake the clutch ECU to make it more robust. Despite the new ECU and the work performed by the machine design team, which can be read about in (TODO REPORT.XX) there was problems with the clutch when it was time to race. The problems was of mechanical nature, where the clutch plate on the ICE side stuck very hard to the center plate of the clutch. When this happened, the ICE  could not be disengaged from the drivetrain. 

To solve this problem, several solutions have been investigated. The clutch mechanism has been controlled by time rather than position. One approach was to use the built in hall sensor in the actuator to control the position. One other idea was to use an external current sensor on the clutch ECU to control the position. A third idea was to continue using time as reference, but increase it so that an end position is always reached, which can be used as a reference position.


\subsection{Internal Combustion Engine}

\section{Results}
\subsection{Competition}

\subsection{End of project}

\section{Conclusion}